\vspace{3cm}Common Crawl

### 2015-10-25 presentation/paper.tex
Finalize section about text extraction

\centering{
    \includegraphics[trim=0 105px 0 0, clip=true, width=.9\textwidth]{images/guardian-website}
}

\scriptsize
\vspace{.1cm}
\url{http://www.theguardian.com/world/2013/jun/09/edward-snowden-nsa-whistleblower-surveillance}

\scriptsize
Edward Snowden: the whistleblower behind the NSA surveillance revelations $|$ US news $|$ The Guardian

\section{jWarcEx}

\begin{lstlisting}[breaklines=true]
Skip to main content

@@

The Guardian, after several days of interviews, is revealing his identity at his request. From the moment he decided to disclose numerous top-secret documents to the public, he was determined not to opt for the protection of anonymity. ``I have no intention of hiding who I am because I know I have done nothing wrong,'' he said.

(...)
\end{lstlisting}

\section{Mozilla Readability.js}

\begin{lstlisting}[breaklines=true]
Edward Snowden: the whistleblower behind the NSA surveillance revelations

@@

The Guardian, after several days of interviews, is revealing his identity at his request. From the moment he decided to disclose numerous top-secret documents to the public, he was determined not to opt for the protection of anonymity. ``I have no intention of hiding who I am because I know I have done nothing wrong,'' he said.

(...)
\end{lstlisting}

\section{Common Crawl}

\begin{lstlisting}[breaklines=true]
Lance Armstrong, Tour de France champ, retires | abc7.com

@@

(...)
\end{lstlisting}

\vspace{.2cm}
\url{http://abc7.com/archive/7962461}

\section{jWarcEx}

\begin{lstlisting}[breaklines=true]
Personalize your weather by entering a location.

@@

\vspace{.2cm}
Sections Traffic Video Los AngelesOrange CountyInland EmpireVentura CountyCalifornia

@@

\quad BREAKING NEWS ABC shows live and on-demand -- Download the WATCH ABC app!

\vspace{.2cm}
Lance Armstrong, Tour de France champ, retires

Seven-time Tour de France champion Lance Armstrong is retiring. He ends his career amidst a federal doping investigation.

February 16, 2011 12:00:00 AM PST

Seven-time Tour de France champion Lance Armstrong said he's retiring from the professional cycling circuit, this time for good. The 39-year-old is calling it ``Retirement 2.0'' and is making it clear there is no reset button this time.

\vspace{.2cm}
He says he wants to spend more time with his children and dedicate himself even more to the fight against cancer with his "Livestrong" Foundation.

(...)
\end{lstlisting}

\vspace{.2cm}
\url{http://abc7.com/archive/7962461}

>>>>

In diesem Abschnitt vergleichen wir die Qualität der Textextraktion von Common Crawl mit dem an der Abteilung für Automatische Sprachverarbeitung der Universität Leipzig entwickelten Tool jWarcEx und Readability.js, das von Mozilla für die Lesenansicht im Firefox-Browser verwendet wird.

Da wir uns bei der Analyse wie oben beschrieben auf die Metadaten beschränken mussten, erfolgte die Analyse stichprobenartig anhand einiger Beispiele, wovon im Folgenden zwei näher erläutert werden.

\section{Beispiel: theguardian.com}

Das erste Beispiel ist der erste Artikel von Glenn Greenwald, Ewen MacAskill und Laura Poitras über Edward Snowden auf \texttt{theguardian.com}\footnote{\url{http://www.theguardian.com/world/2013/jun/09/edward-snowden-nsa-whistleblower-surveillance}}:

\begin{center}
    \includegraphics[trim=0 130px 0 0, clip=true, width=.8\textwidth]{images/guardian-website}
\end{center}

\noindent
Common Crawl und jWarcEx extrahieren in diesem Fall den exakt gleichen Text, der im Wesentlichen der DOM-Eigenschaft \texttt{textContent} entspricht und z.\,B. auch Elemente der Seitennavigation und Alternativtexte von Medien (vlg. Hinweis zum Video) enthält.

Readability.js extrahiert dagegen exakt den Text des Artikel. Die Überschrift und die Autoren werden aus den entsprechenden HTML-Meta-Tags entnommen, wobei hier fälschlicherweise nur das letzte author-Tag beachtet wird.

\begin{minipage}[t]{.5\textwidth}
    \centering{\textbf{Common Crawl / jWarcEx}}
    \vspace{.5cm}
    \scriptsize
    \begin{lstlisting}[breaklines=true]
    Skip to main content

@@

    The Guardian, after several days of interviews, is revealing his identity at his request. From the moment he decided to disclose numerous top-secret documents to the public, he was determined not to opt for the protection of anonymity. "I have no intention of hiding who I am because I know I have done nothing wrong," he said.

    (...)
    \end{lstlisting}
\end{minipage}%
\begin{minipage}[t]{.5\textwidth}
    \centering{\textbf{Readability.js}}
    \vspace{.5cm}
    \scriptsize
    \begin{lstlisting}[breaklines=true]

@@

    The Guardian, after several days of interviews, is revealing his identity at his request. From the moment he decided to disclose numerous top-secret documents to the public, he was determined not to opt for the protection of anonymity. "I have no intention of hiding who I am because I know I have done nothing wrong," he said.

    (...)
    \end{lstlisting}
\end{minipage}

\section{Beispiel: abc7.com}

Unterschiede zwischen der Textextraktion von Common Crawl und jWarcEx zeigen sich z.\,B. an einem Artikel über das Karriereende von Lance Armstrong auf \texttt{abc7.com}\footnote{\url{http://abc7.com/archive/7962461}}.

So erkennt jWarcEx die zu einem Menüpunkt gehörenden Unterpunkte und fasst diese zusammen, während Common Crawl damit teilweise Probleme hat. Außerdem fügt Common Crawl manchmal den Seitentitel an den Anfang des Extraktes hinzu.

\vspace{.5cm}
\begin{minipage}[t]{.5\textwidth}
    \centering{\textbf{Common Crawl}}
    \vspace{.5cm}
    \scriptsize
    \begin{lstlisting}[breaklines=true]
    Lance Armstrong, Tour de France champ, retires | abc7.com

@@

    (...)
    \end{lstlisting}
\end{minipage}%
\begin{minipage}[t]{.5\textwidth}
    \centering{\textbf{jWarcEx}}
    \vspace{.5cm}
    \scriptsize
    \begin{lstlisting}[breaklines=true]

@@

    Sections Traffic Video Los AngelesOrange CountyInland EmpireVentura CountyCalifornia

@@

    BREAKING NEWS ABC shows live and on-demand -- Download the WATCH ABC app!

    (...)
    \end{lstlisting}
\end{minipage}
